Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-09 manuscript.Rmd
10 min bins

Visual inspection of \@ref(fig:part2overall) indicated two extreme outliers, marked by a gray square and a gray diamond. We closely investigated each of the two outliers to understand why their agreement was so much worse compared with the other sessions. The "gray square" outlier had significant confusion between sitting and supine classification. Reviewing the video indicated that this participant spent a long period of time in a seating device that was reclined almost exactly at 45 degrees, making it difficult to determine if the infant was sitting or supine. The infant also spent a long time in mother's arms in an ambiguous supine/sitting position that was hard to classify. This participant's proximal accuracy was also poor because similar ambiguous appeared during the initial recording. In contrast, the "gray diamond outlier" had strong proximal accuracy, with confusion only arising in the distal period between upright and held categories. Reviewing the video showed that all disagreements occurred when the infant was in a baby walker; human coders scored this as "upright" but the models predicted it as "held". Most likely, the infant's movements in the baby walker were more similar to how a baby moved while carried, and unlike how most infant's moved while walking upright.

What is notable about both outliers is that disagreements were restricted to a particular border case (supine vs. sitting; upright vs. held) and their accuracy for other classes was strong. This suggests that their poor performance came as a result of spending a long time in an ambiguous position, not the result of the entire model failing to generalize to the later time period (or an error in sensor placement, such as if the parent removed the leggings and put them on backwards after a diaper change). To better capture the typical level of agreement, we report all correlations in Table \@ref(tab:pt2overalltable) excluding the two outliers. Overall agreement among the non-outlier sessions was excellent for both group models (*r* = `r group_agree_cor_noout`) and individual models (*r* = `r split_agree_cor_noout`). With the exception of held, within-class agreement was strong for the other four body positions.

@@

### Distal Comparison Agreement at a Finer Timescale

>>>>

Visual inspection of Figure \@ref(fig:part2overall) indicated two extreme outliers, which we marked by a gray square and a gray diamond. We closely investigated each of the two outliers to understand why their agreement was below the standard of the other sessions. The "gray square" outlier had significant confusion between sitting and supine classification. Reviewing the video indicated that this participant spent a long period of time in a seating device that was reclined almost exactly at 45 degrees, making it difficult to determine if the infant was sitting or supine. The infant also spent a long time in mother's arms in an ambiguous supine/sitting position that was hard to classify. This participant's proximal accuracy was also poor because similar ambiguous appeared during the initial recording. In contrast, the "gray diamond outlier" had strong proximal accuracy, with confusion only arising in the distal period between upright and held categories. Reviewing the video showed that all disagreements occurred when the infant was in a baby walker; human coders scored this as "upright" but the models predicted it as "held". Most likely, the infant's movements in the baby walker were more similar to how a baby moved while carried, and unlike how most infant's moved while walking upright.

What is notable about both outliers is that disagreements were restricted to a particular border case (supine vs. sitting; upright vs. held); accuracy for other classes remained strong. This suggests that their poor performance came as a result of spending a long time in an ambiguous position, not the result of the entire model failing to generalize to the later time period (or an error in sensor placement, such as if the parent removed the leggings and put them on backwards after a diaper change). To better capture the typical level of agreement, we report all correlations in Table \@ref(tab:pt2overalltable) excluding the two outliers. Overall agreement among the non-outlier sessions was excellent for both group models (*r* = `r group_agree_cor_noout`) and individual models (*r* = `r split_agree_cor_noout`). With the exception of held, within-class agreement was strong for the other four body positions.

@@

### Short-Timescale Agreement during the Distal Comparison

Collecting real-time data that can be synchronized to other sources is a key goal in our development of long-form body position classification. Although overall aggregate agreement in the distal comparison was strong, it is important to show that similarly strong agreement is found within a shorter timescale. We repeated agreement analysis, correlating human-coded body position prevalence with model-predicted prevalence, after dividing the distal comparison period into nine 10-min bins (marked by vertical dashed lines in Figure \@ref(fig:exemplar-timeline)).
